---
output: github_document
---

# despair


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "80%",
  fig.align = "center",
  warning = FALSE
)
```

# Overview

`despair` is a package inspired by Shakespeare's work and his well-known pessimism. It allows the user to create short, clever codes called bard–bits inspired by Shakespeare's work and use daily (de)motivational quotes for personal use or to share with others.

## Installation

You can install this package on CRAN

``` r
install.packages("despair")
```
You can also install the development version of this package through the `devtools` package.
```r
devtools::install_github("jpmonteagudo28/despair")
```

## Usage

There are three basic functions in the package: demotivate, motivate, and bard.bits. Each function will take a category input and an optional numeric or character seed for reproducible results.

```{r example, eval=FALSE}
library(despair)

#> Get info on package version 
 despair.message()
#> despair string generated by {despair} v.0.1.0.R version 4.3.2 (2023-10-31 ucrt).

demotivate()
#> "I’m not really good at advice. Can I interest you in a sarcastic comment?"
demotivate("science", seed = 123)
#> "No matter how hard you try, you’ll always be within one standard deviation of average."
demotivate("science", seed = "lanky poodle")
#> "Don't worry! There might be a socio-anthropoligical intepretation of your results"

motivate("lit")
#> "If you tell the truth, you don't have to remember anything. — Mark Twain"
motivate("religion", seed = 123)
#> "The Christian does not think God will love us because we are good, but that God will make us good because He loves us. - C.S. Lewis"
motivate("religion", seed = "bewildered pooh")
#> "Really great things, when discussed by little men, can usually make such men grow big. - Augustine of Hippo"

bard.bits()
#> "brownish purple kite"
bard.bits("character", seed = 123)
#> "filthy duncan"
bard.bits("character", seed = "stinky chihuahua")
#> "lofty tranio"
```

